A Critical Appraisal of the Zero-Multiple Method: Structural, Thermodynamic, Dielectric, and Dynamical Properties of a Water System

### 2014-11-23 writedown/zm/paper.water/main.tex
improve

The neighbor lists were updated every 5 time-steps. {\color{red} The Gromacs
by default uses the group cut-off scheme, while the ZM method suggests an
atom cut-off scheme~\cite{fukuda2011molecular,fukuda2013zero}.} [{%
\color{blue} COMMENT: I am confusing. Is "rcoulomb"="rlist" default in
gromacs? If so, "Gromacs by default uses the group cut-off scheme" is
correct. Or, here, you want to say the "neighbor list making" is done by
group cut-off? (I reread your "cutoff.pdf")} \recheck{the default is rcoulomb = rlist. both
the neighbor list making and the force computing are in group manner.
I prefer not describing this issue in the paper in detail, because the reader
may not be familiar with the terminology (rlist, rcoulomb, and so on) and
the mechanism behind. I think describing how to use ZM correctly in gromacs is enough.
}] The difference between these
cut-off schemes is discussed in detail in e.g.~Ref.~\cite%
{hunenberger1998alternative,baumketner2009removing}. We adopted the atom
based cut-off scheme in the simulations using the SPME (short-range part)
and ZM electrostatic methods. In order to mimic the atom cut-off scheme in
the Gromacs group cut-off implementation, the radius for neighbor list
updating was set ${0.3}$~nm larger than the cut-off radius (the maximum of
Coulomb cut-off and the van der Waals cut-off).

@@

The short-range part of SPME method was cut-offed at $1.9$~nm, and was
smoothed in a shell of $0.05$~nm width by the Gromacs \textquotedblleft 
\texttt{pme-switch}\textquotedblright\ method. The reciprocal space grid
spacing was set to $0.06$~nm, with B-Spline interpolation order of $6$.
These parameters were chosen to be more accurate than the Gromacs default
choices (grid spacing $0.12$~nm and interpolation order $4$).
The conducting boundary condition was used with SPME.
The splitting parameter was optimized by the error estimate, which is
implemented in Gromacs by tool \textquotedblleft \texttt{g\_pme\_error}%
\textquotedblright ~\cite{wang2010optimizing}. The optimized real space and
reciprocal space force computing errors were equally distributed as $%
1.4\times 10^{-4}$~kJ/(mol nm). Since the magnitude of the forces are of
order $10^{2}$~kJ/(mol nm), this force computing precision almost reaches
the limit of the single-precision representation of the floating point
numbers. % [ {\color{blue} COMMENT: Did you use the
% conducting boundary conditions? (maybe it is default in gromacs.) Please
% state the thing.}]

The ZM method was implemented in Gromacs with the tabulated electrostatic
interaction. A home-made code was used to generate the interaction tables. {%
\color{blue} }$\bigstar $

In the simulations using RF method, the electrostatic interactions were cut-off in the
group manner (Gromacs default), so the radius for neighbor list updating is set identical to
the cut-off radius. [{\color{blue} COMMENT: Is "rcoulomb"="rlist" default
  for RF? If so, please describe it.} \recheck{Describing "rcoulomb"="rlist" by human languange} ]
\recheck{We used $1.2$~nm for both of them}, and the experimental dielectric constant $%
\varepsilon _{\text{rf}}=80$.

@@

\begin{figure}[tbp]
\centering
\includegraphics[]{fig/nvt.pressure.1/pressure-methods.eps}
\caption{The pressure convergence with respect to the cut-off radius. The ZM
methods with order from 1 to 4 are compared with the RF. The splitting
parameter of ZM method is set to be $\protect\alpha =0.00\,\text{nm}^{-1}$.
The black solid line indicates the magnitude of the correct pressure: 1~Bar.
The error bars present the statistical uncertainty at 95\% confidence level. 
{\color{red} This uncertainty is twice of the standard deviation of the
estimates (which are averages along MD trajectories) that is calculated by
the block average method~\protect\cite{janke2002statistical}.} [ {\ 
\color{blue}It maybe good to repeat such explanation in Sec.IIIA.}].[{\ 
\color{blue} another COMMENT: In these figures, can we see the statistical
uncertainty of the pressure obtained by the SPME? Viz., I found no error
bars for SPME.} \recheck{NO SPME result is given in this figure!}]}
\label{fig:pres-comp}
\end{figure}

@@

>>>>

[{%
\color{blue} COMMENT: I am confusing. Is "rcoulomb"="rlist" default in
gromacs? If so, "Gromacs by default uses the group cut-off scheme" is
correct. Or, here, you want to say the "neighbor list making" is done by
group cut-off? (I reread your "cutoff.pdf")} \recheck{
In the main text I only mention the ``group cut-off'' and ``atom cut-off'' and
put how to implement them in the Appendix.  So those who are not familiar with Gromacs would not be confused by the Gormacs terminology (e.g. rlist, rcoulomb, ...).
see the revise below:
}]

The neighbor lists were updated every 5 time-steps. The Gromacs
by default uses the group cut-off scheme, while the ZM method suggests an
atom cut-off scheme~\cite{fukuda2011molecular,fukuda2013zero}. The difference between these
cut-off schemes is discussed in detail in e.g.~Ref.~\cite%
{hunenberger1998alternative,baumketner2009removing}. We adopted the atom
based cut-off scheme in the simulations using the SPME (short-range part)
and ZM electrostatic methods, \recheck{while group cut-off scheme for RF.
  We treated RF differently because the group cut-off scheme is the default scheme in Gromacs.}
\recheck{The implementation details of the atom cut-off scheme in Gromacs are proivded in Appendix.~\ref{app:cut-off}.}

% In order to mimic the atom cut-off scheme in
% the Gromacs group cut-off implementation, the radius for neighbor list
% updating was set ${0.3}$~nm larger than the cut-off radius (the maximum of
% Coulomb cut-off and the van der Waals cut-off).

@@

The short-range part of SPME method was cut-offed at $1.9$~nm, and was
smoothed in a shell of $0.05$~nm width by the Gromacs \textquotedblleft 
\texttt{pme-switch}\textquotedblright\ method. The reciprocal space grid
spacing was set to $0.06$~nm, with B-Spline interpolation order of $6$.
These parameters were chosen to be more accurate than the Gromacs default
choices (grid spacing $0.12$~nm and interpolation order $4$).
The conducting boundary condition was used with SPME.
The splitting parameter was optimized by the error estimate, which is
implemented in Gromacs by tool \textquotedblleft \texttt{g\_pme\_error}%
\textquotedblright ~\cite{wang2010optimizing}. The optimized real space and
reciprocal space force computing errors were equally distributed as $%
1.4\times 10^{-4}$~kJ/(mol nm). Since the magnitude of the forces are of
order $10^{2}$~kJ/(mol nm), this force computing precision almost reaches
the limit of the single-precision representation of the floating point
numbers. % [ {\color{blue} COMMENT: Did you use the
% conducting boundary conditions? (maybe it is default in gromacs.) Please
% state the thing.}]
\recheck{The ZM method was implemented in Gromacs with the tabulated electrostatic
interaction, and the interaction tables were generated by a home-made code.
The experimental dielectric consistency  $\varepsilon _{\text{rf}}=80$
was adopted for the RF method.}

% In the simulations using RF method, the electrostatic interactions were cut-off in the
% group manner (Gromacs default), so the radius for neighbor list updating is set identical to
% the cut-off radius. [{\color{blue} COMMENT: Is "rcoulomb"="rlist" default
%   for RF? If so, please describe it.} \recheck{Describing "rcoulomb"="rlist" by human languange} ]
% \recheck{We used $1.2$~nm for both of them}, and the experimental dielectric constant $%
% \varepsilon _{\text{rf}}=80$.

@@

\begin{figure}[tbp]
\centering
\includegraphics[]{fig/nvt.pressure.1/pressure-methods.eps}
\caption{The pressure convergence with respect to the cut-off radius. The ZM
methods with order from 1 to 4 are compared with the RF. The splitting
parameter of ZM method is set to be $\protect\alpha =0.00\,\text{nm}^{-1}$.
The black solid line indicates the magnitude of the correct pressure: 1~Bar.
The error bars present the statistical uncertainty at 95\% confidence level. 
{\color{red} This uncertainty is twice of the standard deviation of the
estimates (which are averages along MD trajectories) that is calculated by
the block average method~\protect\cite{janke2002statistical}.} [ {\ 
\color{blue}It maybe good to repeat such explanation in Sec.IIIA.}].[{\ 
\color{blue} another COMMENT: In these figures, can we see the statistical
uncertainty of the pressure obtained by the SPME? Viz., I found no error
bars for SPME.} \recheck{NO SPME result is given in this figure, 1 Bar is the target pressure.}]}
\label{fig:pres-comp}
\end{figure}

@@

\section{Implementation of atom cut-off scheme in Gromacs}
\label{app:cut-off}

The Gromacs code 4.6 does not directly 
support the atomistic cut-off scheme for tabulated electrostatic interaction that is
needed for ZM method. The atom cut-off scheme can be implemented
by using the default ``\texttt{Group}'' neighbor searching method, while setting
the radius of neighbor list ``\texttt{rlist}'' 0.3~nm larger than the cut-off radius,
which is the maximum of the electrostatic cut-off ``\texttt{rcoulomb}'' and the van der Waals cut-off ``\texttt{rvdw}''.
Due to the buffering region that is of thickness 0.3~nm, the atom cut-off scheme in Gromacs is in general more expensive than the group cut-off scheme.
